### 2023-02-23 code/translocation_survival_analysis_suppl.Rmd
Add error bars and remove background from figures

d1 %>% 
  mutate(period = factor(period, levels = c("before", "after"))) %>% 
  ggplot(aes(x = period, y = log10(bd_load + 1))) +
    geom_boxplot() + 
    labs(x = "Period", y = "Bd load (log10(bd_load + 1))") +
    facet_grid(. ~ site_id1) +
    theme(axis.text.x = element_text(angle = 90))
ggsave(here::here("doc", "manuscript", "figures", "bdload_beforeafter.png"), width = 5, height = 3)
```

>>>>

d1 %>% 
  mutate(period = factor(period, levels = c("before", "after"))) %>% 
  ggplot(aes(x = period, y = log10(bd_load + 1))) +
    geom_boxplot() + 
    labs(x = "Period", y = "Bd load (log10(bd_load + 1))") +
    facet_grid(. ~ site_id1) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5),
          strip.text.x = element_text(size = 8),
          panel.grid = element_blank())
ggsave(here::here("doc", "manuscript", "figures", "bdload_beforeafter.png"), width = 6, height = 3)
```

### 2023-02-23 code/translocation_survival_exploratory.Rmd
Add error bars and remove background from figures

```{r retrieve-frog-survival-data}
files <- fs::dir_ls(here::here("data", "raw", "cmr-analysis", "survival"), glob = "*_cohort.csv")
cohort_survival <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts site_id as numeric string from file path
  rename(years_since_intro = years_since_introduction) %>% 
  filter(years_since_intro == 1) %>% 
  select(site_id, release_date, years_since_intro, median_survival)
rm(files)
```

@@

cohort_survival %>% 
  mutate(release_year = year(release_date)) %>% 
  group_by(site_id) %>% 
  summarize(plot_survival = mean(median_survival)) %>%  # create variable by which to order sites for plotting
  arrange(plot_survival) %>% 
  mutate(siteid_order = row_number()) %>% 
  inner_join(cohort_survival, by = "site_id") %>% 
  inner_join(donors, by = "site_id") %>% 
  select(-plot_survival) %>% 
    ggplot(aes(x = reorder(site_id, siteid_order), y = median_survival, group = donor)) +  # reorder site_id by siteid_order)
      geom_point(aes(color = donor), size = 3) +
      scale_color_manual(values = palette1) + 
      labs(x = "Recipient site", y = "1-year frog survival")
```
* Strong effect of site/translocation on frog survival.
* Survival is highly variable across sites, but highly repeatable within a site. 
* Indicates need to include site_id and/or translocation_id as group-level effect(s).

>>>>

```{r retrieve-frog-survival-data}
files <- fs::dir_ls(here::here("data", "raw", "cmr-analysis", "survival"), glob = "*_cohort.csv")
cohort_survival <- read_csv(files, id = "path") %>% 
  mutate(site_id = str_extract(path, "(\\d)+"), .after = path) %>%  # extracts site_id as numeric string from file path
  rename(years_since_intro = years_since_introduction) %>% 
  filter(years_since_intro == 1) %>% 
  select(site_id, release_date, years_since_intro, median_survival, lo_survival, hi_survival)
rm(files)
```

@@

cohort_survival_plot <- cohort_survival %>% 
  mutate(release_year = year(release_date)) %>% 
  group_by(site_id) %>% 
  summarize(plot_survival = mean(median_survival)) %>%  # create variable by which to order sites for plotting
  arrange(plot_survival) %>% 
  mutate(siteid_order = row_number()) %>% 
  inner_join(cohort_survival, by = "site_id") %>% 
  inner_join(donors, by = "site_id") %>% 
  select(-plot_survival) %>% 
    ggplot(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor)) +  # reorder site_id by siteid_order)
      geom_errorbar(aes(ymin = lo_survival, ymax = hi_survival), color = "black", width = 0.15, position = position_dodge2(width = 0.3)) +
      geom_point(size = 3) +
      scale_color_manual(values = palette1) + 
      labs(x = "Recipient site", y = "1-year frog survival") +
      theme_classic() +
      theme(
        legend.background = element_rect(color = "black", size = 0.3),
        legend.position = c(0.2, 0.8),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

cohort_survival_plot

# Unable to dodge points and error bars together using position_dodge and group = site_id. Why?
```
* Strong effect of site/translocation on frog survival.
* Survival is highly variable across sites, but highly repeatable within a site. 
* Indicates need to include site_id and/or translocation_id as group-level effect(s).

### Save plot

```{r}
ggsave(here::here("doc", "manuscript", "figures", "translocation_survival_bysiteid.png"), width = 5, height = 5) 
```

### 2023-02-23 doc/manuscript/translocation.qmd
Add error bars and remove background from figures

^4^Department of Environmental Science, Policy, and Management, University of California.
Berkeley, Berkeley, CA, 94720-3114

^5^Museum of Vertebrate Zoology, University of California, Berkeley, Berkeley, CA, 94720-3160

@@

<!--# The following point was made in the original outline but is not included in P3, P4, or P5. Could be useful to include when introducing translocations in Results: Translocation of individuals from putatively resistant populations to sites that were formerly occupied but from which populations were extirpated by disease provides a way to disentangle the contributions of natal environment and host genetics on host persistence and recovery. -->

@@

<!--# Let's revisit whether the selection results should go here or at the end of the results. Putting those results here would reduce the need to describe populations as "putatively resistant". Mark W: Agreed. -->

@@

<!--# Mark W: As I am reading through the results, our sections do not allude to the Allie's section.  We should discuss how our sections can set-up Allie's section with a few well-chosen words throughout.  -->

@@

Given demographic stochasticity (i.e., probabilistic births and deaths of individuals in a population) and environmental variability in the probability of juvenile recruitment to adults $\omega$, our model predicted that, following a single introduction of 40 adult individuals into a population, the six populations with the highest adult survival probabilities had 50-year extinction probabilities of less than 1 (@fig-viability B).
Therefore, even under conservative assumptions about recruitment probability $\omega$ (a parameter where ), these populations had some probability of persistence over 50 years following a single introduction.
For these six populations, as $\omega$ increased from 0.1 to 0.3, 50 year extinction probability was less 0.5, indicating strong potential for long-term persistence in the presence of Bd and environmental variability in recruitment success (@fig-viability B).
In contrast, for the six populations where $\sigma_{A_R} < 0.5$, extinction probability over 50 years was always predicted to be 1.
To test the validity of our model predictions, we demonstrated that our stochastic model could describe the general recovery trajectory of our translocated population with the longest survey history (@fig-viability-supp B; population 70550, surveyed for 16 years).
Overall, our model demonstrates that given observed yearly adult survival probabilities of resistance frogs in non-natal locations, 50% of our translocated populations have a high probability of population growth and long-term viability in the presence of Bd.

<!--# To help constrain the possible values of omega, add information about recruitment probability observed in the study populations? Because we don't have accurate counts of subadults, can we even provide rough estimate of recruitment probability?  Mark W here: This would be great. If we have even ballpark estimates of \omega it would be useful to include.-->

@@

@@

![Median survival of each cohort of translocated frogs to the 12 recipient sites included in this study. Sites are arranged along the x-axis using the average of the median 1-year survival per translocation at each site. Frog survival was estimated using capture-mark-recapture methods. Dot colors indicate the donor population from which frogs in each translocated cohort were collected. <!--# Include error bars on these median estimates. -->](figures/translocation_survival_bysiteid.png){#fig-translocation-survival width="450"}

>>>>

^4^Department of Environmental Science, Policy, and Management, University of California - Berkeley, Berkeley, CA, 94720-3114

^5^Museum of Vertebrate Zoology, University of California - Berkeley, Berkeley, CA, 94720-3160

@@

@@

<!--# Add Allie's selection results here -->

@@

@@

Given demographic stochasticity (i.e., probabilistic births and deaths of individuals in a population) and environmental variability in the probability of juvenile recruitment to adults $\omega$, our model predicted that, following a single introduction of 40 adult individuals into a population, the six populations with the highest adult survival probabilities had 50-year extinction probabilities of less than 1 (@fig-viability B).
Therefore, even under conservative assumptions about recruitment probability $\omega$ (a parameter where ), these populations had some probability of persistence over 50 years following a single introduction.
For these six populations, as $\omega$ increased from 0.1 to 0.3, 50 year extinction probability was less 0.5, indicating strong potential for long-term persistence in the presence of Bd and environmental variability in recruitment success (@fig-viability B).
In contrast, for the six populations where $\sigma_{A_R} < 0.5$, extinction probability over 50 years was always predicted to be 1.
To test the validity of our model predictions, we demonstrated that our stochastic model could describe the general recovery trajectory of our translocated population with the longest survey history (@fig-viability-supp B; population 70550, surveyed for 16 years).
Overall, our model demonstrates that given observed yearly adult survival probabilities of resistance frogs in non-natal locations, 50% of our translocated populations have a high probability of population growth and long-term viability in the presence of Bd.
<!--# Add text to the end of this paragraph that refers to higher survival of cohorts translocated later in the 2006-2020 study period (Table 2), to make the case that more than 50% of future cohorts are expected to have high survival. -->

@@

<!--# The following point was made in the original Introduction outline but ultimately not addressed there: Translocation of individuals from putatively resistant populations to sites that were formerly occupied but from which populations were extirpated by disease provides a way to disentangle the contributions of natal environment and host genetics on host persistence and recovery. -->

@@

![Median survival of each cohort of translocated frogs to the 12 recipient sites included in this study. Sites are arranged along the x-axis using the average of the median 1-year survival per translocation at each site. Frog survival was estimated using capture-mark-recapture methods. Dot colors indicate the donor population from which frogs in each translocated cohort were collected. Error bars show the 2.5% and 97.5% posterior quantiles (i.e., 95% uncertainty intervals). <!--# Unable to dodge points and associated error bars together using group. Any help with this? Code is in translocation_survival_exploratory.Rmd -->](figures/translocation_survival_bysiteid.png){#fig-translocation-survival width="450"}
